Analytical Uncertainty Quantification for Multilevel Mediation Analysis

### 2024-07-16 papers/Manuscript - Exact Asymptotics.tex
Add short discussion of simultaneous estimation of mediation effects

>>>>

While the above discussion focuses on estimation of each mediation effect individually, it is straightforward to extend our analysis to simultaneous estimation of, for example, the total, direct and indirect effects on a single scale. This has the advantage of estimating covariances between mediation effects, rather than just the effects' marginal variances.
